Exploring Feature Engineering

### 2019-03-22 Scripts/evaluating_correlations.Rmd
editted correlation script

  data <- readRDS(datadir)
  colnames(data) <- gsub(paste("_", predictortype, sep=""),"",colnames(data))

@@

```{r}
corfunction(cl = "K562", resolution = "25kb", predictortype = "count", annotation = "chromstates")
corfunction(cl = "K562", resolution = "25kb", predictortype = "count", annotation = "histones")
corfunction(cl = "K562", resolution = "25kb", predictortype = "count", annotation = "tfbs")

>>>>

  data <- readRDS(datadir)

  if(predictortype=="dist"){
    #performing log2 transformation on distances
    data <- apply(data,2,function(x){log(x + 1, base=2)})
  }

  colnames(data) <- gsub(paste("_", predictortype, sep=""),"",colnames(data))

@@

```{r}
corfunction(cl = "K562", resolution = "10kb", predictortype = "count", annotation = "chromstates")
corfunction(cl = "K562", resolution = "10kb", predictortype = "count", annotation = "histones")
corfunction(cl = "K562", resolution = "10kb", predictortype = "count", annotation = "tfbs")

corfunction(cl = "K562", resolution = "10kb", predictortype = "perc", annotation = "chromstates")
corfunction(cl = "K562", resolution = "10kb", predictortype = "perc", annotation = "histones")
corfunction(cl = "K562", resolution = "10kb", predictortype = "perc", annotation = "tfbs")

corfunction(cl = "K562", resolution = "10kb", predictortype = "dist", annotation = "chromstates")
corfunction(cl = "K562", resolution = "10kb", predictortype = "dist", annotation = "histones")
corfunction(cl = "K562", resolution = "10kb", predictortype = "dist", annotation = "tfbs")

corfunction(cl = "K562", resolution = "25kb", predictortype = "count", annotation = "chromstates")
corfunction(cl = "K562", resolution = "25kb", predictortype = "count", annotation = "histones")
corfunction(cl = "K562", resolution = "25kb", predictortype = "count", annotation = "tfbs")
